Scheduling and Amortization for MPC

### 2021-12-13 paper_SIMD.tex
minor comments

\ishaq{We need to think of a way to handle 4th case for def-use, when a nested block B def is followed by another, different, nested block B' use. Note: The handwritten notes say we can break it into 2 edges. One idea to this end is to insert a def' node which is a copy of the original def. The def' should be placed in a block that contains both B and B'.}

@@

\ishaq{Naive question: Which index of $\texttt{min}_{1}[\stackrel{\rightarrow}{i}]$ would contain the minimum, how are we reducing it?}

@@

\ishaq{For our rader: Such dependencies will not involve phi nodes only. e.g. $a[i] = a[i] + a[i-1]$}

@@

\ishaq{I don't think I understand closures. Why does the closure for $\texttt{index}_0[i]$ include $\texttt{c}[\stackrel{\rightarrow}{i}]$ but the closure for $\texttt{index}_0[i] = \phi(\texttt{index}_1[i-1], -1)$ not include $\texttt{p}$.}

@@

Consider a loop $j$ enclosed in some fixed $\underline{i}$. Only if an update (definition) $\texttt{A}_m[f(i,j,k)] = ... $ at some iteration $\underline{j}$ 
references the \emph{same} array element as an use $ ... = \texttt{A}_n[f'(i,j,k)]$ at some later iteration $\underline{j}'$, 
we may have a loop-carried dependence for $\texttt{A}$ due to this def-use pair. (In contrast, Cytron's algorithm inserts a loop-carried dependency every time there is an array update.)
The algorithm above examines all def-use pairs in loop $j$, including defs and uses in nested loops, searching for values $\underline{i}, \underline{j}, \underline{j}', \underline{k}, \underline{k}'$ that satisfy 
$f(\underline{i},\underline{j},\underline{k}) = f'(\underline{i},\underline{j}',\underline{k}')$. If such values exist for some def-use pair, then there is a potential 
loop-carried dependence on $\texttt{A}$; otherwise there is not and we can remove the spurious backward edge thus ``freeing up'' statements for vectorization. \ana{Double check this!!!}

>>>>

\ishaq{We need to think of a way to handle 4th case for def-use, when a nested block B def is followed by another, different, nested block B' use. Note: The handwritten notes say we can break it into 2 edges. One idea to this end is to insert a def' node which is a copy of the original def. The def' should be placed in a block that contains both B and B'.}
\ishaq{THE ABOVE COMMENT IS RESOLVED. After transformation to SSA, there should be an intermediate variable (phi node) that is assigned a value depending on whether control branched or not. Should we put this into the writeup?}

@@

@@

\ishaq{For our radar: Such dependencies will not involve phi nodes only. e.g. $a[i] = a[i] + a[i-1]$}

@@

@@

\ishaq{Note to self: This algorithm is an instantiation for $j$ loop, the one for $k$ loop will be exactly the same, modulo variable name.}.

Consider a loop $j$ enclosed in some fixed $\underline{i}$. Only if an update (definition) $\texttt{A}_m[f(i,j,k)] = ... $ at some iteration $\underline{j}$ 
references the \emph{same} array element as a use $ ... = \texttt{A}_n[f'(i,j,k)]$ at some later iteration $\underline{j}'$, 
we may have a loop-carried dependence for $\texttt{A}$ due to this def-use pair. (In contrast, Cytron's algorithm inserts a loop-carried dependency every time there is an array update.)
The algorithm above examines all def-use pairs in loop $j$, including defs and uses in nested loops, searching for values $\underline{i}, \underline{j}, \underline{j}', \underline{k}, \underline{k}'$ that satisfy 
$f(\underline{i},\underline{j},\underline{k}) = f'(\underline{i},\underline{j}',\underline{k}')$. If such values exist for some def-use pair, then there is a potential 
loop-carried dependence on $\texttt{A}$; otherwise there is not and we can remove the spurious backward edge thus ``freeing up'' statements for vectorization. \ana{Double check this!!!}
